Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-09 doc/paper.Rmd
some edits to definition profiles

The Chumbley score  provides us with another approach in the same-source assessment of bullet striation marks. \citet{chumbley} compare two toolmarks for same-source. The data for this study was obtained from 50 sequentially manufactured screwdriver tips. \citet{chumbley} report error rates for markings made by the tips at different angles. For markings made under a 30 degree the authors  report an average false negative error rate of 0.023  and an average false positive error rate of 0.09. For other angles the error rates for false negatives stay the same while the rate of false positives decreases to 0.01. \hh{are the angles steeper?} 
The paper by \citet{hadler} is based on the same data but the authors focus on  markings made under the same angle. The error rates associated with the deterministic version of the score are  0.06 for false  negatives and a false positive error rate of 0.

@@

Comparisons of striae from bullets are usually based on comparisons of striae in land engraved areas, which are extracted in form of cross sections, called *profiles* \citep{aoas,ma2004}. From profiles bullet *signatures* \citep{chu2013,aoas} are extracted as residuals of a loess fit or Gaussian filter.
 Signatures are considered to be noise free and a good reflection of the key attributes of the raw marking, and the unique features of a bullet. \hh{Do you have a reference for the previous sentenced?} A  detailed discussion of the extraction technique for signatures is given in \citet{aoas}.
 <!--, where comprehensive details about the height at which profile is to be selected, removing curvature, smoothing, identifying groove locations are explained.-->

>>>>

The Chumbley score  provides us with another approach in the same-source assessment of bullet striation marks. \citet{chumbley} compare two toolmarks for same-source. The data for this study was obtained from 50 sequentially manufactured screwdriver tips. \citet{chumbley} report error rates for markings made by the tips at different angles. For markings made at 30 degree the authors  report an average false negative error rate of 0.089  and an average false positive error rate of 0.023. For other angles of 60 and 85 degrees the false negatives error rate is 0.09 while the rate of false positives decreases to 0.01. The paper by \citet{hadler} is based on the same data but the authors focus on  markings made under the same angle. The error rates associated with the deterministic version of the score are  0.06 for false  negatives and a false positive error rate of 0.

@@

Comparisons of striae from bullets are usually based on comparisons of striae in land engraved areas, which are extracted in form of cross sections, called *profiles* \citep{aoas,ma2004}. From profiles bullet *signatures* \citep{chu2013,aoas} are extracted as residuals of a loess fit or Gaussian filter. This effectively removes topographic structure from the data in the attempt to increase the signal to noise ratio. The span of the loess fit was found using cross-validation, as described by \citet{aoas}.
 <!-- Signatures are considered to be noise free and a good reflection of the key attributes of the raw marking, and the unique features of a bullet. \hh{Do you have a reference for the previous sentenced?} A  detailed discussion of the extraction technique for signatures is given in \citet{aoas}. -->
 <!--, where comprehensive details about the height at which profile is to be selected, removing curvature, smoothing, identifying groove locations are explained.-->
